lifespan_eda

### 2025-01-31 eda/lifespan_eda.Rmd
remove rain plot

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data, data.table, nlme, devtools, slider, see, broom.mixed, ggrain, ggpubr)

@@

```{r}
full_rain <- final_df %>%
  mutate(continent = factor(case_when(country == "India" | country == "China" | country == "Singapore" | country == "Japan" ~ "Asia",
                               country == "USA" | country == "Canada" ~ "North America",
                               country == "Brazil" ~ "South America",
                               country == "Australia" ~ "Australia",
                               TRUE ~ "Europe"))) %>%
  ggplot(aes(x=continent, y=age_years, fill=sex)) +
  geom_rain(alpha=.5, violin.args = list(scale="count", alpha=.5),
            point.args=list(alpha=.2)) +
  theme_linedraw(base_size = 14) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom") +
  guides(fill=guide_legend(title="Sex")) + 
  coord_fixed(ratio=.08) +
  labs(y="Age (Years)")
```

@@

fig5A <- ggarrange(sample_boxplot2, country_leg,
          sample_barplot2,  sex_leg,
          nrow=2, ncol=2, 
          #align = "v", 
          common.legend = FALSE,
          legend = "none",
          widths=c(8, 1),
          heights=c(1.9, 1)
          )
```

```{r}
fig5_AB <- ggarrange(fig5A, full_rain,
          nrow=1, ncol=2, 
          #legend = "none",
          widths=c(1.8, 1),
          labels = "AUTO")
fig5_AB
saveRDS(fig5_AB, file="../figs/figure_5_AB.rds")
ggsave("../figs/fig5_ab.jpeg", fig5_AB, width=18, height=10, units="in")
```

>>>>

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data, data.table, nlme, devtools, slider, see, broom.mixed, ggpubr)

@@

@@

fig5A <- ggarrange(sample_boxplot2, country_leg,
          sample_barplot2,  sex_leg,
          nrow=2, ncol=2, 
          #align = "v", 
          common.legend = FALSE,
          legend = "none",
          widths=c(8, 1),
          heights=c(1.9, 1)
          )
saveRDS(fig5A, file="../figs/figure_5_A.rds")
```
